Changes in gene expression associated with transitions in reproductive meristem identity during early development of rice inflorescence.

### 2015-12-09 ms.Rmd
Changed title (issue #25)

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage[utf8]{inputenc}
  \DeclareUnicodeCharacter{2265}{$\geq$}
output:
  BiocStyle::html_document:
    dev: CairoPDF
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
    toc: yes
bibliography: bib/papersLib.bibtex
---

>>>>

---
title: Changes in gene expression associated with transitions in reproductive meristem identity during early development of rice inflorescence.
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage[utf8]{inputenc}
  \DeclareUnicodeCharacter{2265}{$\geq$}
output:
  BiocStyle::html_document:
    dev: CairoPDF
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
    toc: yes
bibliography: bib/papersLib.bibtex
---
